### 2019-12-15 article.tex
Some grammatical improvements and average mean detail added

\begin{algorithm}
	\caption{data preparation}
	\label{alg:preprocessing}
	\begin{algorithmic}
		\INPUT{raw fMRI images}
		\STATE 
		\STATE For each fMRI scan following pre-processing steps had been done.
		\STATE

@@

	\end{algorithmic}
\end{algorithm}

@@

Furthermore, our model's accuracy can be obtained in two different aspects. The first one would be the correctness of each time-slice prediction ($\overline{C}_{i,t}$), while the second, is the accuracy of disease diagnosis ($\overline{C}_i$), and we are mostly interested in the later. Both of the mentioned statistics can be calculated using Equation \eqref{eq:meanCorrectness}.

@@

\begin{eqnarray}
\label{eq:meanCorrectness}
\overline{C_{i,t}} &=& {{\sum_{i=1}^{m} \sum_{t=1}^{T (=198)} C_{i,t} } \over {m \times T} } \\ 
\overline{C_i} &=& {{\sum_{i=1}^{m} C_i } \over {m } }  \nonumber 
\end{eqnarray}

@@

\begin{table}
	\label{table:averageAccuracies}
	\caption{Average accuracies for different tests}
	\begin{tabular}{ c | c | c }
		\hline
		$i$ & $\overline{C_{i,t}}\;(\%)$ & $\overline{C_i}\;(\%)$ \\ 
		test no. & mean time-slice accuracy & mean accuracy \\ \hline
		1 & 100 & 100 \\
		2 & 97.90 & 100 \\
		3 & 74.83 & 83.33 \\
		4 & 96.30 & 100 \\
		5 & 97.14 & 100 \\
		6 & 100 & 100 \\
		7 & 98.65 & 100 \\
		8 & 78.87 & 83.33 \\
	\end{tabular}
\end{table}

>>>>

\begin{algorithm*}
	\caption{Data preparation}
	\label{alg:preprocessing}
	\begin{algorithmic}
		\INPUT{raw fMRI images}
		\STATE 
		\STATE For each fMRI scan following pre-processing steps had been done.
		\STATE

@@

	\end{algorithmic}
\end{algorithm*}

@@

Furthermore, our model's accuracy can be obtained in two different aspects. The first one would be the correctness of each time-slice prediction ($\overline{C}_{T}$), while the second, is the accuracy of disease diagnosis ($\overline{C}$), and we are mostly interested in the later. Both of the mentioned statistics can be calculated using Equations \eqref{eq:meanTimeSliceCorrectness} and \eqref{eq:meanCorrectness}.

@@

\begin{eqnarray}
\label{eq:meanTimeSliceCorrectness}
\overline{C_{T}} &=& {{\sum_{i=1}^{m} \sum_{t=1}^{T (=198)} C_{i,t} } \over {m \times T} } \\ 
\label{eq:meanCorrectness}
\overline{C} &=& {{\sum_{i=1}^{m} C_i } \over {m } } 
\end{eqnarray}

@@

Table \ref{table:averageAccuracies} shows a summary of 8 different tests. We can define the average of mean accuracies as Equations \eqref{eq:averageMeanTimeSliceCorrectness} and \eqref{eq:averageMeanCorrectness} in order to use them as a measure that shows how the model is performing in the case of accuracy.

\begin{eqnarray}
\label{eq:averageMeanTimeSliceCorrectness}
\mathbf{C_t} &=& {{\sum_{j=1}^{J} \overline{C_{T}} } \over {J} } \\ 
\label{eq:averageMeanCorrectness}
\mathbf{C} &=& {{\sum_{j=1}^{J} \overline{C} } \over {J} } 
\end{eqnarray}

\begin{table}
	\caption{Average accuracies for different tests}
	\begin{tabular}{ c | c | c }
		\hline
		$j$ & $\overline{C_{i,t}}\;(\%)$ & $\overline{C_i}\;(\%)$ \\ 
		test no. & mean time-slice accuracy & mean accuracy \\ \hline
		1 & 100 & 100 \\
		2 & 97.90 & 100 \\
		3 & 74.83 & 83.33 \\
		4 & 96.30 & 100 \\
		5 & 97.14 & 100 \\
		6 & 100 & 100 \\
		7 & 98.65 & 100 \\
		8 & 78.87 & 83.33 \\ \hline
		Average & $\mathbf{C_t} = $ 92.96 & $\mathbf{C} = $ 95.83 \\
	\end{tabular}
\label{table:averageAccuracies}
\end{table}
